Formalization and Automation of Variants of G\"{o}del's Ontological Proof of God's Existence

### 2013-08-16 Abstract/GodProof-Abstract.tex
Number the lemmas and theorems
some further modifications

From these axioms and definitions we then infer:
\begin{enumerate}
\item Positive properties are possibly exemplified.
\item Possibly God exists.
\item If x is God-like, then the property of being 
God-like is an essence of x.
\item Necessarily God exists.
\end{enumerate}

@@

\item A formalization using the Isabelle proof assistant \cite{Isabelle} partially automated with Sledgehammer \cite{ToDo} and Metis \cite{ToDo}.
\end{itemize}

G\"{o}del's proof is challenging to formalize and verify 
because it requires very expressive logical languages with 
modal operators (\emph{possibily} and \emph{necessarily}) and higher-order quantifiers. 
Our computer-assisted formalizations rely on an embedding of the modal logic S5 
into classical higher-order logic with Henkin 
semantics \cite{J23} and 
employed recently developed interactive and automated deduction tools designed for this logic.

@@

Future work includes an
extensive study of other formalizations of ontological arguments with
our machinery.

>>>>

From these axioms and definitions we then infer:

\begin{description}
\item {(L1)} Positive properties are possibly exemplified.
\item {(L2)} Possibly God exists.
\item {(L3)} If x is God-like, then the property of being 
God-like is an essence of x.
\item {(T)} \ Necessarily God exists.
\end{description}

@@

\item A formalization using the Isabelle proof assistant \cite{Isabelle} partially automated with Sledgehammer \cite{Sledgehammer} and Metis \cite{Hurd03first-orderproof}.
\end{itemize}

G\"{o}del's proof is challenging to formalize and verify 
because it requires very expressive logical languages with 
modal operators (\emph{possibily} and \emph{necessarily}) and higher-order quantifiers. 
Our computer-assisted formalizations rely on an embedding of the modal logic S5 
into classical higher-order logic with Henkin 
semantics \cite{J23,B9} and 
employed recently developed interactive and automated deduction tools designed for this logic.

@@

Future work includes an extensive study of other formalizations of
ontological arguments with our machinery. Variations of the
distinctive features of the base logic S5 (e.g. non-rigid symbols, 
varying domains, etc.) are enabled in these studies due
to the flexibility of the embeddings based approach.
